Tables

### 2019-12-12 manuscript/supplementary.Rmd
figure rearrange
lime figures converted to tables

---
title: Supplementary information
output: 
  pdf_document:
    keep_tex: false
---

@@

@@

site_correction_factors %>%
  kable(caption = 'Descriptor correction factors at each site')
```

\newpage

@@

```{r PDIlimeAnalysisPlot}
loadd(PDI_lime_analysis_plot)

PDI_lime_analysis_plot
```

```{r DAIlimeAnalysisPlot,fig.height=8}
loadd(DAI_lime_analysis_plot)

DAI_lime_analysis_plot
```

>>>>

---
title: Supplementary information
output: 
  pdf_document:
    keep_tex: false
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
---

@@

```{r phenotypic_descriptors,cache=FALSE}
loadd(phenotypic_descriptor_info)

phenotypic_descriptor_info %>%
  kable(format = 'latex',booktabs = TRUE)
```

@@

site_correction_factors %>%
  mutate_if(is.double,signif,digits = 3) %>%
  kable(caption = 'Descriptor correction factors at each site')
```

@@

### 2019-12-12 manuscript/tables.Rmd
added to descriptor table
lime figures converted to tables

---
title: Tables
output: pdf_document
---

## Tables

@@

```{r phenotypic_descriptors,cache=FALSE}
loadd(phenotypic_descriptor_info)

phenotypic_descriptor_info %>%
  kable(format = 'markdown')
```

```{r resampled_results}

```

>>>>

---
title: Tables
output: 
  pdf_document:
    includes:
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
---

@@

```{r PDI_lime_results}
loadd(PDI_lime_analysis_table)

PDI_lime_analysis_table %>%
  kable(format = 'latex',booktabs = TRUE,escape = FALSE,caption = ' ') %>%
  collapse_rows(columns = 1:3, latex_hline = "major", valign = "middle")
```

```{r DAI_lime_results}
loadd(DAI_lime_analysis_table)

DAI_lime_analysis_table %>%
  kable(format = 'latex',booktabs = TRUE,escape = FALSE,caption = ' ') %>%
  collapse_rows(columns = 1:3, latex_hline = "major", valign = "middle")
```
